---
title: "MetaG-heatmap-Binder"
subtitle: "SUBTITLE"
author: "Laetitia and Guillaume"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# System Info

```{r}
# session info
sessionInfo()
```

# Data

```{r}
# data
MAGnum <- read.delim("input_matrix_v1.txt")
rownames(MAGnum) <- MAGnum[,1]
counts <- MAGnum[,-1]
counts[,1]
MAGcountsNum <- sapply(counts, as.numeric)
```

# Plot

# data

```{r}
MAGnum_df <- read.delim("input_matrix_v2.txt") %>%
    tibble::column_to_rownames(var = "X")

MAGnum_mat <- MAGnum_df %>%
    data.matrix()

heatmap(MAGnum_mat)

breakers <- seq(min(MAGnum_mat, na.rm = T), 
                max(MAGnum_mat, na.rm = T), 
                length.out = 51)

my_palette <- colorRampPalette(c("red","white ", "blue"))(n = 299)

heatmap.2(MAGnum_mat, 
        distfun = function(x) dist(x, method = "euclidean"),
        hclustfun = function(x) hclust(x,method = "complete"),
        scale = "row",
        col = my_palette, 
        #breaks = breakers, 
        trace = "none",
        key = TRUE, symkey = FALSE, 
        density.info = "none", srtCol = 30,
        margins=c(5.5,7), cexRow = 1.25,cexCol = 1.25,
        key.xlab = "MAG Abundance",
        #ColSideColors = colz,
        lhei = c(1.5,9), 
        key.title=NA
        )

